RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-03-01 main.tex
:triangular_flag_on_post: JSAC 230301

	% \begin{subsection}{Related Works}
	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \qty{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
	However, it severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.

@@

\begin{section}{RIScatter}
	\begin{subsection}{Principles}
		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		An antenna scatterer first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		An ideal metamaterial scatterer reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift on top.
		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
		In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and an antenna mode component that depends on the impedance mismatch \cite{Hansen1989}.
		The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.
		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
		% A natural question is, is it possible to use a scatterer
		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos}.
		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
			\subfloat[Input Distribution]{
					\input{assets/illustration/input_distribution.tex}
				\label{fg:input_distribution}
			\\
			\subfloat[Reflection Pattern]{
					\input{assets/illustration/time_structure.tex}
				\label{fg:time_structure}
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
				% RIScatter node transmit symbol \num{1}
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
			\label{fg:scatter_comparison}
			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
			% There are many ways to order
			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
	We choose $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{e3} channel realizations.

@@

		\begin{subsubsection}{Convergence}
			\begin{figure}[!t]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\input{assets/simulation/wsr_convergence.tex}
				}
				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
				\label{fg:wsr_convergence}
			\end{figure}

@@

			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=e3$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		% However, the primary rate benefit
		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \gls{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\qty{-40}{\dBm}$ and $r=\qty{2}{\meter}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

>>>>

	% \begin{subsection}{Related Works}
	As a special case of \gls{cr}, active and passive transmissions coexist and interplay in \gls{ambc} and \gls{sr}.
	Such a coexistence is classified into commensal (overlay), parasitic (underlay), and competitive (interfering) paradigms, and their achievable rate and outage performance were investigated in \cite{Guo2019b,Ding2020}.
	For the co-located cooperative receiver, the \gls{ber} performance of \gls{ml}, linear, and \gls{sic} detectors are derived over flat fading channels \cite{Yang2018}.
	However, the work assumed equal symbol duration and perfect synchronization for primary and backscatter links.
	Importantly, active-passive coexisting networks have three special and important properties:
	\begin{enumerate}
		\item Primary and backscatter symbols are superimposed by \emph{double modulation} (i.e., multiplication coding);
		\item Backscatter signal strength is much weaker than primary due to the \emph{double fading} effect;
		\item The spreading factor (i.e., backscatter symbol duration over primary) is usually large\footnote{The load-switching interval of low-power backscatter modulators is usually \num{0.1} to \SI{10}{\us} \cite{Torres2021}, accounting for a typical spreading factor between \num{10} and \num{e3}.}.
	\end{enumerate}
	The second property motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to view \gls{sr} as a multiplicative \gls{noma} and perform \gls{sic} from primary to backscatter link.
	During primary decoding, the backscatter signal can be modelled as channel uncertainty or multiplicative interference when the spreading factor is large or small, respectively.
	Decoding each backscatter symbol also requires multiple \gls{sic} followed by a \gls{mrc} and is operation-intensive and \gls{csi}-sensitive.
	% Such a \gls{sic} receiver is operation-intensive and \gls{csi}-sensitive because it involves $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
	When the spreading factor is sufficiently large, the primary achievable rate under semi-coherent detection\footnote{In this paper, semi-coherent detection refers to the primary/backscatter decoding with known \gls{csi} and unknown backscatter/primary symbols.} asymptotically approaches its coherent counterpart and both links are decoded interference-free \cite{Long2020a}.
	% However, it significantly increases \gls{sic} operations per backscatter symbol and severely limits the backscatter \emph{throughput}.
	However, this severely limits the backscatter throughput and requires numerous \gls{sic} per backscatter symbol.

@@

\begin{section}{RIScatter}
	\begin{subsection}{Principles}
		\gls{rf} wave scattering/reflecting are often manipulated by passive antennas or programmable metamaterial \cite{Liang2022}.
		% can be described by a unified signal model and implemented by passive antennas or programmable metamaterial \cite{Liang2022}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		% An antenna-based scatterer usually consists of an integrated antenna, a load-switching modulator, an energy harvester, and on-chip components (e.g., microcontroller and sensors) \cite{Dobkin2012}.
		The former first receives the impinging signals then reradiates some back to the space and dissipates the remaining \cite{Dobkin2012}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		% In comparison, a typical metamaterial-based scatterer comprises an outer metamaterial layer of numerous sub-wavelength metallic/dielectric patches (with tunable permittivity/permeability), a middle copper plate layer that avoids leakage, an inner circuit board layer that adjusts patch responses, and an integrated microcontroller/\glsentryshort{fpga} for coordination and control \cite{Wu2020}.
		In contrast, the latter reflects the wave at the space-metamaterial boundary without receiving them and mainly applies a phase shift.
		% In practice, both types of scatterers have {finite} reflection states with non-zero reflection loss.
		% In general, the scattered signal consists of a structural mode component that consistently contributes to environment multipath and can be modelled within \gls{csi}, and an \emph{antenna} mode component that depends on the impedance mismatch and can be used for backscatter modulation and/or passive beamforming \cite{Hansen1989}.
		The scattered signal consists of a structural mode component that consistently contributes to environment multipath (usually modelled within \gls{csi}) and an antenna mode component that depends on the impedance mismatch (mainly used for backscatter modulation and/or passive beamforming) \cite{Hansen1989}.
		% The former is usually modelled within \gls{csi} while the latter is mainly used for backscatter modulation and/or passive beamforming.
		For an antenna (resp. metamaterial) scatterer with $M$ reflection states, the reflection coefficient at state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is
		\begin{equation}
			\Gamma_m = \frac{Z_m - Z^*}{Z_m + Z},
			\label{eq:reflection_coefficient}
		\end{equation}
		where $Z_m$ is the antenna load (resp. metamaterial unit) impedance at state $m$ and $Z$ is the antenna input (resp. medium characteristic) impedance.

		\gls{bc} treats scatterers as information sources that \emph{randomly} choosing the reflection state based on information symbol.
		For $M$-ary \gls{qam}, constellation point $c_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Thomas2012a}
		\begin{equation}
			\Gamma_m = \alpha \frac{c_m}{\max_{m'} \lvert c_{m'} \rvert},
			\label{eq:backscatter_modulation}
		\end{equation}
		where $\alpha \in \mathbb{I}$ is the common amplitude scattering ratio at the direction of interest.
		In contrast, \gls{ris} treats scatterers as channel adaptors that \emph{deterministically} choosing the reflection state based on \gls{csi}.
		For a \gls{ris} element with $M$ available states, phase shift $\theta_m$ maps to reflection coefficient $\Gamma_m$ by \cite{Wu2018}
		\begin{equation}
			\Gamma_m = \beta_m \exp(j \theta_m),
			\label{eq:passive_beamforming}
		\end{equation}
		where $\beta_m \in \mathbb{I}$ is the overall amplitude scattering ratio at state $m$.\footnote{Most existing \gls{ris} literature assumes lossless reflection $\beta_m=1$, $\forall m$.}
		% A natural question is, is it possible to use a scatterer
		For a scatter node with given load impedance set, \gls{bc} employs $\Gamma_m$ only as an information codeword while \gls{ris} employs $\Gamma_m$ only as a passive beamforming codeword.
		RIScatter generalizes both from a probabilistic perspective where each node \emph{semi-randomly} chooses the reflection state with the guidance of probability $P(\Gamma_m)$.
		The input distribution is flexibly designed as a joint function of the information source, \gls{csi}, and \gls{qos} of both links.
		\gls{bc} and (static) \gls{ris} can be regarded as its extreme cases where the input distribution boils down to uniform and degenerate, respectively.
		Fig.~\ref{fg:scatter_comparison} compares the input distribution and reflection pattern of RIScatter to \gls{bc} and \gls{ris}.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fg:input_distribution}
			}
			\\
			\subfloat[Reflection Pattern]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_structure.tex}
				}
				\label{fg:time_structure}
			}
			\caption{
				Input distribution and reflection pattern of scattering applications.
				``PB'', ``BB'', and ``CB'' refer to primary symbol block, backscatter symbol block, and channel block, respectively.
				Shadowing means presence of primary link.
				In this example, the optimal passive beamformer is state \num{2} and its input probability for RIScatter is \num{0.75}.
				% RIScatter node transmit symbol \num{1}
				The spreading factor is \num{4} for RIScatter and \num{8} for \gls{ambc}/\gls{sr}.
			}
			\label{fg:scatter_comparison}
		\end{figure}
		\begin{remark}
			RIScatter is different from conventional dynamic passive beamforming since the reflection pattern conveys additional information.
			% There are many ways to order
			% The latter only involves time sharing between different states but there are many ways to ensure within a channel block.
			The latter only involves time sharing between different states and the actual order has no impact on the (ergodic) primary performance.
			For RIScatter, different state combinations correspond to different messages and the impact reduces to dynamic passive beamforming upon successful backscatter decoding.
			% However, different combinations correspond to different backscatter messages and RIScatter impact is determined dynamic passive beamforming once successfully decoded.
		\end{remark}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the considered RIScatter system.
	We assume the AP-user distance is \SI{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\SI{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\SI{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\SI{30}{\dB}$ is the reference path loss at $d_0=\SI{1}{\meter}$, $\kappa$ is the Rician K-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$.
	We set $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{e3} channel realizations.

@@

		\begin{subsubsection}{Convergence}
			\begin{figure}[!t]
				\centering
				\resizebox{0.75\columnwidth}{!}{
					\input{assets/simulation/wsr_convergence.tex}
				}
				\caption{Typical convergence curves at $\rho=0$ for $Q=4$, $K=8$, $M=2$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
				\label{fg:wsr_convergence}
			\end{figure}

@@

			\caption{Typical achievable rate region/points of scattering applications for $Q=1$, $K=1$, $M=4$, $N=\num{e3}$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and the strategies above.
		% \emph{First,} we observe both \gls{bbc} and \gls{sr} achieves when the spreading factor $N$ is sufficiently large.
		\emph{First,} we observe \gls{bbc} and \gls{sr} achieve the best backscatter performance thanks to coherent decoding.
		% However, \gls{sr} requires $N$ \gls{sic} followed by a \gls
		% However, \gls{sr} requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol and the cost can be prohibitive.
		For \gls{sr}, this comes with the cost of $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} per backscatter symbol.
		% However, the primary rate benefit
		% For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmmac} \eqref{eq:dmmac} has lower error probabilities.
		% For \gls{sic}-based \gls{sr}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		% However, the primary rate is only maintained at a very large spreading factor, which significantly constrains the backscatter \emph{throughput}.
		\emph{Second,} the average primary rate slightly decreases/increases in the presence of a \gls{ambc}/\gls{ris} node and the benefit of \gls{sr} is not obvious.
		This is because the cascaded channel is usually orders of magnitude weaker than the direct channel.
		\gls{ris} always ensures constructive superposition of direct and scattered components while \gls{sr} only creates a quasi-static rich-scattering environment that marginally enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than multipath components and the \gls{sr} point should move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff with adaptive input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others using deterministic reflection pattern.
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is lower than \gls{bbc} and \gls{sr} but higher than \gls{ambc}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent energy detection, and the adaptive channel coding of RIScatter provides better performance than equiprobable inputs of \gls{ambc} especially at the low \gls{snr} of double fading.
		When multiple antenna is available at the \gls{ap}, active beamforming can be optimized for RIScatter nodes and the backscatter rate gain over \gls{ambc} can be even larger.
	\end{subsection}

	\begin{subsection}{Input Distribution under Different \gls{qos}}
		\begin{figure}[!t]
			\centering
			\resizebox{0.65\columnwidth}{!}{
				\input{assets/simulation/distribution_weights.tex}
			}
			\caption{Typical RIScatter reflection state distribution at different $\rho$ for $Q=1$, $K=1$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.}
			\label{fg:distribution_weights}
		\end{figure}
		The objective is to demonstrate RIScatter nodes can leverage \gls{csi}- and \gls{qos}-adaptive input distribution design to balance backscatter modulation and passive beamforming.
		For one RIScatter node with $M=4$, we evaluate the \gls{kkt} input distribution\footnote{Problem \eqref{op:input_distribution} is convex when $K=1$ and the \gls{kkt} solution is global optimal.} at different \gls{qos} and present the result in Fig.~\ref{fg:distribution_weights}.
		At $\rho=0$ where the backscatter performance is prioritized, the optimal input distribution is \num{0} on two states and nearly uniform on the other two.
		This is inline with Shannon's observation that binary antipodal inputs can be good enough for channel capacity at the low \gls{snr} \cite{Shannon1948}.
		Due to the weak scattered signal, the conditional energy \gls{pdf} under different hypotheses can be closely spaced as in Fig.~\ref{fg:energy_distribution}.
		The extreme states producing the lowest/highest energy are always assigned with non-zero probability and the middle ones may not provide enough energy difference and thus end up unused.
		At $\rho=1$ where the primary performance is prioritized, the optimal input distribution is \num{1} at the state that maximizes the primary \gls{snr} and \num{0} at the others.
		That is, the reflection pattern becomes deterministic and the RIScatter node boils down to a discrete \gls{ris} element.
		Increasing $\rho$ from \num{0} to \num{1} provides a smooth transition from backscatter modulation to passive beamforming and proves RIScatter unifies \gls{bc} and \gls{ris} from a probabilistic perspective.
	\end{subsection}

	\begin{subsection}{Rate Region by Different Schemes}
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution, $Q=1$\label{fg:region_distribution}]{
				\resizebox{0.6\columnwidth}{!}{
					\input{assets/simulation/region_distribution.tex}
				}
			}
			\\
			\subfloat[Active Beamforming, $Q=4$\label{fg:region_beamforming}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_beamforming.tex}
				}
			}
			\subfloat[Decision Threshold, $Q=4$\label{fg:region_threshold}]{
				\resizebox{0.48\columnwidth}{!}{
					\input{assets/simulation/region_threshold.tex}
				}
			}
			\caption{
				Average primary-total-backscatter rate regions by different input distribution, active beamforming, and decision threshold schemes for $K=2$, $M=4$, $N=20$, $\sigma_v^2=\SI{-40}{\dBm}$ and $r=\SI{2}{\meter}$.
			}
		\end{figure}
		\begin{subsubsection}{Input Distribution}
			We compare these input distribution designs for problem \eqref{op:input_distribution}:
			\begin{itemize}
				\item \emph{Cooperation:} Joint nodes encoding using a $K$-dimensional probability array $P_{\mathcal{K}}(x_{m_{\mathcal{K}}})$ by Algorithm \ref{al:input_distribution};
				\item \emph{Exhaustion:} Exhaustive search over the $M$-dimensional probability simplex with resolution $\Delta p = \num{e-2}$;
				\item \emph{\gls{kkt}:} Numerical \gls{kkt} evaluation by Algorithm \ref{al:input_distribution};
				\item \emph{Equiprobable:} Uniform input distribution for all nodes.
			\end{itemize}
			For dispersed nodes, joint encoding is inapplicable and we consider these independent input distribution recovery methods (from the joint probability array):
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors by \texttt{Tensor Toolbox} \cite{Bader2022};
				\item \emph{Randomization:} Gaussian randomization with the guidance of correlation matrix \cite{Calvo2010}.
				% guided by correlation matrix \cite{Calvo2010}.
			\end{itemize}

			Fig.~\subref*{fg:region_distribution} shows the average achievable rate regions for those designs.
			We observe Cooperation provides the outer bound and joint encoding can be beneficial.
			The average rate performance of Exhaustion and \gls{kkt} completely coincide with each other, demonstrating \gls{kkt} input distribution is favorable for a moderate $K$ as mentioned in Remark \ref{re:input_kkt_distribution}.
			Equiprobable experiences minor backscatter and major primary rate losses without exploiting \gls{csi} and \gls{qos}.
			Both rate gaps should be larger when $M$ and/or $K$ increase.
			For the recovery methods, the simple Marginalization provides a close performance to \gls{kkt}, but Randomization and Decomposition fail our expectations for most channel realizations.
			Those observations emphasize the importance of (joint) adaptive RIScatter encoding and demonstrate the advantage of the proposed \gls{kkt} input distribution design.
		\end{subsubsection}
